### 2015-07-14 intro-new.tex
first complete version after fixing most of the stuff

Most of Internet traffic is content, and most of Internet connected hosts are mobile. A key example of the content-dominated nature of Internet is that online video accounts for nearly 70\% of traffic today and is expected to grow to nearly 80\% by 2018 \cite{cisco-videogrowth}. The evidence of a highly mobile Internet is that 5B mobile devices connect to the Intenet today and thet generate more traffic than wired devices \cite{cisco-vni}.

@@

A content-dominated, highly mobile Internet needs several forms of infrastructure support. It needs network switches and links with sufficient capacity to carry traffic to end users. It needs servers to sustain and accelerate delivery of content. It also needs an infrastructure to help establish and maintain connections in the presence of high network moblity or changing of addresses. The focus of this thesis is to design \emph{services} that manage the resources on such infrastructures towards achieving the desired goals.

@@

\textbf{Cost-intensive} There is a substantial captial and operational cost in running a large-scale infrastructure \cite{greenberg2008cost}, and which causes a sigificant reduction in the profit margins of the infrastructure owner. A prominent example of low-profit infrastructures are Internet service provider networks \cite{isp-low-profit}. Cost reduction while meeting performance and other constraints is a central design problem that we address in this thesis.

\textbf{Geo-distributed:} These infrastructures are often highly geo-distribtued, e.g., a large internet service provider (ISP) or a content delivery network (CDN) has Points-of-Presence (POP) at hundreds of locations \cite{dilley2002globally}. Thus, it is necessary that services be designed to leverage geo-distributed deployments for reducing user-perceived latencies.

@@

Due to their geo-distributed deployment, these infrastructure services commonly make three sets of decisions: \emph{content placement}, \emph{request redirection}, and \emph{network routing}. As each of these decisions can be made relatively independently of others, we call them ``degrees of freedom'' available to a service.

@@

Geo-distribtued infrastructure and workload locality makes content placement a powerful degree of freedom. Workload locality implies that a content is typically popular in only a few regions at any given time, and as a result only a few replicas of a content are sufficient to reduce user-perceived latency for most users. Further, the geo-distribued infrastructure enables these few replicas to be placed close to regions of demand, thereby achieving a good tradeoff between user-perceived latency and infrastructure cost. We illustrate with a couple of examples why placement can be a more powerful degree of freedom than redirection and routing in designing infrastructure services.

@@

\textbf{Placement vs. routing:} Content placement is more powerful than routing because it can change the \emph{traffic matrix} for which the routing is to be computed. A traffic matrix is a 2-dimensional matrix representing the demand in the network. The $i,j$-th entry in this matrix is the traffic from node $i$ to node $j$ in the network topology \cite{fortz2000internet}.  Let us take an example traffic matrix for which routing is to be computed (Figure \ref{fig:placement-routing}). Content placement can turn any traffic matrix into a null matrix (one whose all entries are zero) provided all content that a node in a network needs is placed at the same node. Such a placement obviates the need to send traffic to any other node, and therefore makes routing a trivial problem. While this is an extreme example, and one may not have sufficient resources to place content at all locations in the network, this example demonstrates that the ability to change the traffic matrix makes content placement more powerful than routing.

@@

We consider three types of infrastructures in this thesis.

\begin{description}
	\item[Internet service provider (ISP):] ISPs perform traffic engineering to achieve several objectives such as cost and congestion reduction, fault tolerance etc. As explained in Section \ref{sec:intro-te}, our work designs and evaluates traffic engineering in content-dominated ISP networks while accounting for its interaction with placement and redirection schemes. 
	\item[Global name service (GNS):] GNS can enable establishing and maintaining connections between mobile entities on the Internet. As explained in Section \ref{sec:intro-gns}, our name service design, Auspice, meets the challenge posed by high mobility, which is to return up to date addresses for billions of mobile names with frequently changing network address.
	\item[Content datacenter (CDC):] Content datacenters are used to store and serve content to end users. As explained in Section \ref{sec:intro-cdc}, our work quantifies the tradeoff between user-perceived performance and energy savings achieved via a coordinated consolidation of servers and switches, and presents the design and implementation of a system to leverage this tradeoff.
\end{description}

\subsection{Traffic engineering in content-dominated networks}
\label{sec:intro-te}
In an ISP network with content-dominated traffic, traffic engineering decisions are not isolated from content placement and request redirection. As above examples show, content placement and request redirection determine the traffic matrix and hence influence traffic engineering. A key question therefore is how should traffic engineering be done in light of the interaction between placement, redirection and routing.

We address the above question in two scenarios. The first scenario in a more common occurence in present day Internet, in which an ISP has little control over placement and redirection. The second scenario is motivated by a recent, potentialy transformative trend: Network CDNs (NCDNs) -- CDNs deployed by ISPs on their infrastructures. Unlike traditional ISPs, NCDNs enjoy full control over placement, redirection and routing on their networks.

@@

We model a content-dominated ISP network by accounting for its content \emph{location diversity} -- the presence of content at multiple network locations, and the ability of end-users to download content from those locations. Location diversity is enabled by several types of applications and services, such as CDNs, P2P, mirrored websites. We create location diversity using a simple content placement scheme -- randomly placing content at multiple locations --, to reflect the limited control of ISPs on content placement in their networks.

@@

There are strong economic factors motivating ISPs to transform into NCDNs for delivering content to users on its network: %falling bandwidth prices due to competition and technology trends, 
potential sources of revenue by selling content-based services to end-users, easy availability of CDN technology in the form of licensed and managed CDNs and reduction in backbone traffic due to content caching via NCDNs \cite{telco-cdn-arguments}. These factors have motivated more than 30 ISPs to deployed NCDNs on their network.

NCDNs represent a paradigm shift in which both content delivery and traffic engineering is handled by a single entity. This change affects the metrics of interest of an NCDN as well the techniques an it can use. While a traditional ISP is concerened with traffic enginerring related objectives such as network link utilization, and a traditional CDN is concered with optimizing user-perceived performance, an NCDN is concered with both these metrics. While a traditional ISP can decide network routing and a traditional CDN can decide placement and redirection, but only an NCDN decides placement, redirection and routing. Besides using existing techniques to handle these tasks independently, an NCDN has the option of jointly optimizing these decisions as well.

%An NCDN controls content delivery related decisions such as placement and redirection in addition to network routing.

@@

\tbd{write motivation here.The effects of Inernet's poor support for mobility are present everywhere:}

A key reason for Internet's poor support for moblity is that communication on the Internet is based on IP addresses that keep changing due to mobility. On the other hand, what remains unchanged is the name or identity of communication end-points. If we can enable communication over names, we can handle mobility. A  global name service (GNS) enable such a name-based communication by maintaining an up-to-date mapping from names to network addresses for all names. Figure \ref{fig:gns-example} illustrates the use of GNS in handling mobility. A mobile user Bob updates the GNS with its new address soon after changing its network address. Alice obtains Bob's new address from the GNS and is able to establish connection with Bob despite Bob's mobilty.

\begin{figure}
	\centering
	\includegraphics[scale=0.4]{fig/gns-example.png}
	\label{fig:gns-example}
	\caption{A global name service helps establish and maintain connections between mobile entities by keeping an up-to-date mapping from their names to their network addresses. \tbd{add bob's mobility to figure}}
\end{figure}

To appreciate the challenges in implementing such a GNS, we discuss the limitation of Internet's existing naming service DNS as a solution for mobility.
\begin{description}
	\item[Passive caching:] 
	DNS relies heavily on passive caching based on TTLs for reducing both system load and client-perceived latency. However, high mobility severely limits effectiveness of TTL-caching. Handling mobility requires up-to-date responses, so the load and client-perceived latency increase with the mobility rate irrespective of the TTL.
	\item[Static placement:] 
	Under high mobility, the latency to an authoritative name server determines user-perceived query latency in the common case. Today, authoritative name server locations are chosen statically irrespective of where the query demand is coming from, which could result in highly sub-optimal query latencies for users querying the name service from a location distant from the statically placed replicas. 
	\item[Hierarchical names:]
	The main proposal to enhance DNS's security, DNSSEC, is dependent on a single root of trust due to DNS's hierarchical design. A root that is tightly controlled today by ICANN and the US Department of Commerce, a state-of-affairs that is inherently anti-competitive and geo-politically problematic. \tbd{clarify more} 
\end{description}

While the first two problems are related to authoritative name servers and can be addressed within the scope of current DNS, the third issue requires a clean slate redesign of the naming system. Below, we first discuss our naming system design followed by a new authoritative name service design.

%Our work makes two main contributions towards addressing the challenges of designing a global name service for high mobility.

@@

\textbf{Auspice name resolution service:} \tbd{revise this paragraph, shorten and connect} A key component of our naming system is Auspice: a scalable geo-distributed service for mapping names to network addresses under high mobility. A key decision in Auspice's design is that of placement of name records that store the name-to-address mapping. The placement problem is challenging due to a fundamental cost-vs.-performance trade-off: placing name record at multiple locations improves latency of content accesses but increases update propagation costs of keeping consistent replicas. To address this challenge, Auspice name resolution service infers pockets of high demand for a name and uses a heuristic placement strategy that selects both the number and location of the replicas in a demand-aware manner to provide low request latency, low update cost, and high availability.  We extensively evaluate Auspice for an expected workload of a global name service and show that it significantly outperforms both commercial managed DNS services as well as DHT-based replication alternatives to DNS. Auspice is deployable in the Internet today as a scalable managed DNS provider, potentially enhacing support for mobility in the present day Internet as well.

\subsection{Energy optimization in content datacenters}
\label{sec:intro-cdc}
Energy use is a key component of operational costs of \emph{content datacenters (CDCs)}, datacenters that are used for storing and serving content to end-users. CDCs can potentially reduce their energy use via consolidation of servers and switches, but in doing so, they risk inflating end-user response times potentially leading to SLA violations. Our primary contribution is to quantify the tradeoff between energy savings via consolidation and response times in CDCs, and the design and implementation of Shrink, a system that aggressively leverages this tradeoff in order to yield significant savings in energy use in CDCs while affecting user-perceived response times in a controlled manner. To our knowledge, Shrink is the first system to consolidate servers and switches in a coordinated manner, an approach that reduces network energy use by up to 42\% compared to network-unaware server consolidation schemes. Our evaluation of Shrink using a workload from a large CDN's datacenter shows that Shrink can reduce energy use by 35\% over a scheme provisioned for the peak demand, while increasing the mean, 95th and 99th percentile response times by 8\%, 3\% and 15\% respectively.

@@

Chapter \ref{ch:te-background}, Chapter \ref{ch:beyondmlu} and Chapter \ref{ch:ncdn} present our research on traffic engineering in content-dominated networks. Chapter \ref{ch:te-background} presents background on traffic engineering, content delivery and the interaction between them. Chapter \ref{ch:beyondmlu} presents a comparison of traffic engineering schemes in a network with location diversity of content. Chapter \ref{ch:ncdn} designs and evaluates traffic engineering and content delivery schemes in a Network CDN.

Chapter \ref{ch:intro-auspice} presents the design, implementation and evaluation of a global name service for a highly mobile Internet.

Chapter \ref{ch:shrink} presents the design, implementaiton and evaluation of Shrink - a system for reducing energy use of content datacenters via server consolidation.

>>>>

Most of Internet traffic is content, and most of Internet connected hosts are mobile. A key example of the content-dominated nature of Internet is that online video accounts for nearly 67\% of traffic today and is expected to grow to nearly 80\% by 2018 \cite{cisco-videogrowth}. The evidence of a highly mobile Internet is that close to 5 billion mobile devices connect to the Intenet today and they generate more traffic than wired devices \cite{cisco-vni}.

@@

A content-dominated, highly mobile Internet needs several forms of infrastructure support. It needs network switches and links with sufficient capacity to carry traffic to end users. It needs servers to sustain and accelerate delivery of content. It also needs  infrastructure to help establish and maintain connections in the presence of high network mobility (or changing of addresses) of connection end-points. The focus of this thesis is to design \emph{services} that manage the resources on such infrastructures towards achieving their desired goals.

@@

\textbf{Cost-intensive} There is a substantial captial and operational cost in running a large-scale infrastructure \cite{greenberg2008cost}, and which causes a sigificant reduction in the profit margins of the infrastructure owner. A prominent example of cost-intensive, low-profit infrastructures are Internet service provider networks \cite{isp-low-profit}. Thus, a main goal of service design is to reduce cost while meeting performance and other constraints.

\textbf{Geo-distributed:} These infrastructures are often highly geo-distribtued, e.g., a large Internet service provider (ISP) or a content delivery network (CDN) has Points-of-Presence (POP) at hundreds of locations \cite{dilley2002globally}. Thus, it is necessary that services be designed to leverage geo-distributed deployments for reducing user-perceived latencies.

@@

Due to their geo-distributed deployment, these infrastructure services commonly make three sets of decisions: \emph{content placement}, \emph{request redirection}, and \emph{network routing}. As each of these decisions can be made relatively independent of others, we call them ``degrees of freedom'' available to a service.

@@

Geo-distribtued infrastructure and workload locality makes content placement a powerful degree of freedom. Workload locality implies that a content is typically popular in only a few regions at any given time, and as a result only a few replicas of a content placed in those regions  are sufficient to reduce user-perceived latency for most users. Further, the geo-distribued infrastructure enables these few replicas to be placed close to regions of demand, thereby achieving a good tradeoff between user-perceived latency and cost of content replication. We illustrate with a couple of examples why placement can be a more powerful degree of freedom than redirection and routing in designing infrastructure services.

@@

\textbf{Placement vs. routing:} Content placement is more powerful than routing because it can change the \emph{traffic matrix} for which the routing is to be computed. A traffic matrix is a 2-dimensional matrix representing the demand in the network. The $i,j$-th entry in this matrix is the traffic from node $i$ to node $j$ in the network topology \cite{fortz2000internet}.  Let us take an example traffic matrix for which routing is to be computed (Figure \ref{fig:placement-routing}). Content placement can turn any traffic matrix into a null matrix (one whose all entries are zero) provided all content that a node in a network needs is placed at the same node. Such a placement obviates sending traffic to any other node, and therefore makes routing a trivial problem. While this is an extreme example, and one may not have sufficient resources to place content at all locations in the network, it demonstrates that the ability to change the traffic matrix makes content placement more powerful than routing.

@@

We study the design of services for the following infrastructures in this thesis.

\begin{description}
	\item[Internet service provider (ISP):] ISPs perform traffic engineering to achieve several objectives such as cost and congestion reduction, fault tolerance etc. As we explain in Section \ref{sec:intro-te}, our work designs and evaluates traffic engineering in content-dominated ISP networks while accounting for its interaction with placement and redirection schemes. 
	\item[Global name service (GNS):] GNS can enable establishing and maintaining connections between mobile entities on the Internet. As we explain in Section \ref{sec:intro-gns}, our name service design, Auspice, meets the challenge posed by high mobility, which is to return up to date addresses for billions of mobile names with frequently changing network address.
	\item[Content datacenter (CDC):] Content datacenters are used to store and serve content to end users. As we explain in Section \ref{sec:intro-cdc}, our work quantifies the tradeoff between user-perceived performance and energy savings achieved via a coordinated consolidation of servers and switches, and presents the design and implementation of a system to leverage this tradeoff.
\end{description}

\subsection{Traffic engineering in content-dominated networks}
\label{sec:intro-te}
In an ISP network with content-dominated traffic, traffic engineering decisions that computer network-layer routing are not isolated from traffic adaptation occuring at application-layer. For example, content placement and request redirection determine the traffic matrix and hence influence traffic engineering. While the interaction between network layer and application adaptation has been studied previously \cite{Roughgarden,selfishQiu,Jiang2009,JohariGameTheory, CATE, P4P}, the distinguishing aspect of our work it to study the role of placement strategies on this interaction.

We design and evaluate traffic engineering schemes in two scenarios that vary in terms of the flexibility of content placement. The first scenario is a more common occurence in present day Internet, in which an ISP has little control over placement and redirection. The second scenario is motivated by a recent, potentialy transformative trend: Network CDNs (NCDNs) -- CDNs deployed by ISPs on their infrastructures. Unlike traditional ISPs, NCDNs enjoy full control over placement, redirection and routing on their networks.

@@

We model a content-dominated ISP network by accounting for its \emph{location diversity} -- the presence of content at multiple network locations, and the ability of end users to download content from those locations. Location diversity is enabled by several types of applications and services, such as CDNs, P2P, mirrored websites. We create location diversity using a simple content placement scheme -- randomly placing content at multiple locations --, to reflect the limited control of ISPs on content placement in their networks.

@@

There are strong economic factors motivating ISPs to transform into NCDNs for delivering content to users on its network: need for additional revenue source in the face of falling bandwidth prices due to competition and technology trends, viability of monetizing NCDNs by selling content-based services to end users, easy availability of CDN technology in the form of licensed and managed CDNs and reduction in backbone traffic due to content caching via NCDNs \cite{telco-cdn-arguments}. These factors have motivated more than 30 ISPs to deployed NCDNs on their network.

NCDNs represent a paradigm shift in which both content delivery and traffic engineering is handled by a single entity. This change affects the metrics of interest of an NCDN as well the techniques it can use. While a traditional ISP is concerened with traffic enginerring related objectives such as network link utilization, and a traditional CDN is concered with optimizing user-perceived performance, an NCDN is concered with both these metrics. While a traditional ISP can decide network routing and a traditional CDN can decide placement and redirection, but only an NCDN decides placement, redirection and routing. Besides using existing techniques to handle these tasks independently, an NCDN has the option of jointly optimizing these decisions as well.

@@

The effects of Inernet's poor support for mobility are present everywhere. Today, it is difficult to initiate connection with a mobile device since there is no global infrastructure to locate it. As a result, mobile communication initiation is mostly unidirectional in the Internet, from the mobile to the fixed hosts. The lack of this basic functionalily has led to application-specific solutions which causes both redundant effort by developers and possibly redundant infrastructure expenditure also. Yet, support for mobility is patchy among applications: SSH sessions terminate unexpectedly, HTTP downloads terminate before completion and VoIP calls get disrupted when network addresses change.

A key reason for Internet's poor support for moblity is that communication on the Internet is based on IP addresses that keep changing due to mobility. On the other hand, what remains unchanged is the name or identity of communication end-points. If we can enable communication over names, we can handle mobility. A  global name service (GNS) enable such a name-based communication by maintaining an up-to-date mapping from names to network addresses for all names. Figure \ref{fig:gns-example} illustrates how GNS helps establish connections in a common mobility scenario. A mobile user Bob changes its network address and updates the GNS with its new address soon after. Another mobile user Alice obtains Bob's new address from the GNS and is able to establish connection with Bob despite Bob's mobilty.

\begin{figure}
	\centering
	\includegraphics[scale=0.4]{fig/gns-example.png}
	\label{fig:gns-example}
	\caption{A global name service helps establish and maintain connections between mobile entities by keeping an up-to-date mapping from their names to their network addresses.}
\end{figure}

To appreciate the challenges in implementing such a GNS, we discuss the limitation of Internet's existing naming service DNS as a solution for mobility.
\begin{description}
	\item[Passive caching:] 
	DNS relies heavily on passive caching based on TTLs for reducing both system load and client-perceived latency. However, high mobility severely limits effectiveness of TTL-caching. Establishing connection under high mobility requires up-to-date knowledge of network addresses, so the load and client-perceived latency increase with the mobility rate irrespective of the TTL.
	\item[Static placement:] 
	Under high mobility, the latency to an authoritative name server determines user-perceived query latency in the common case. Today, authoritative name server locations are chosen statically irrespective of where the query demand is coming from, which could result in highly sub-optimal query latencies for users querying the name service from a location distant from the statically placed replicas. 
	\item[Hierarchical names:]
	DNS uses a hierarchical design of namespace as well as federation structure. Due to DNS's hierarchical design, the main proposal to enhance DNS's security, DNSSEC, is dependent on a single root of trust. 
\end{description}

While the first two problems are related to authoritative name servers and can be addressed within the scope of current DNS, the third issue requires a clean slate redesign of the naming system. Below, we first discuss our naming system design followed by a new authoritative name service design that supports high mobility.

@@

\textbf{Auspice name resolution service:} Auspice is a scalable, geo-distributed service for resolving names to their network address, both represented in any format,  under high mobility. The flexibility of name and address formats makes Auspice deployable in the Internet as a scalable managed DNS provider, potentially enhacing support for mobility in the present day Internet as well.

Auspice reduces \emph{time-to-connect} to highly mobile names by providing their up-to-date addresses with a low latency.
A key insight underlying Auspice is a demand-aware placement of name records, which store name-to-address mapping. The demand-aware placement heuristic adapts the set of replicas for a name record based on read-to-write ratios, overall system load and the geo-distribtution of demand for a name record to provide low latency name-to-address lookups in a cost-effective manner. Our experimental evaluation shows that Auspice's demand-aware placement enables it to significantly outperform commercial managed DNS services, DHT-based replication alternatives to DNS and static placement policies such as random-$k$ and replicate-all, which use the same request redirection policy as Auspice.

\subsection{Energy optimization in content datacenters}
\label{sec:intro-cdc}
Energy use is a key component of operational costs of \emph{content datacenters (CDCs)}, datacenters that are used for storing and serving content to end users. CDCs can potentially reduce their energy use via consolidation of servers and switches, but in doing so, they risk inflating end user response times potentially leading to SLA violations. Our primary contribution is to quantify the tradeoff between energy savings via consolidation and response times in CDCs, and the design and implementation of Shrink, a system that aggressively leverages this tradeoff in order to yield significant savings in energy use in CDCs while affecting user-perceived response times in a controlled manner. A key reason for the small user-perceived performance impact is that despite server consolidation, a simple placement strategy achieves a cache hit rate near to an unconsolidated datacenter. To our knowledge, Shrink is the first system to consolidate servers and switches in a coordinated manner, an approach that reduces network energy use by up to 42\% compared to network-unaware server consolidation schemes. Our evaluation of Shrink using a workload from a large CDN's datacenter shows that Shrink can reduce energy use by 35\% over a scheme provisioned for the peak demand, while increasing the mean, 95th and 99th percentile response times by 8\%, 3\% and 15\% respectively.

@@

In the first part, which includes Chapter \ref{ch:te-background}, Chapter \ref{ch:beyondmlu} and Chapter \ref{ch:ncdn}, we present our research on traffic engineering in content-dominated networks. Chapter \ref{ch:te-background} presents background on traffic engineering, content delivery and the interaction between traffic engineering and application-layer adaptation, and motivates the key research questions we address on this topic. Chapter \ref{ch:beyondmlu} presents a comparison of traffic engineering schemes in a network with location diversity of content. Chapter \ref{ch:ncdn} designs and evaluates traffic engineering and content delivery schemes in a Network CDN.

The second part, which includes Chapter \ref{ch:intro-auspice}, presents the design, implementation and evaluation of Auspice -- a global name service for a highly mobile Internet.

The second part, which includes Chapter \ref{ch:shrink}, presents the design, implementaiton and evaluation of Shrink - a system for reducing energy use of content datacenters via a coordinated consolidation of servers and switches.

### 2015-07-14 ncdnpaper/Conclusions.tex
added abstract, small reference fixes in rest of thesis.
first complete version after fixing most of the stuff

\section{Conclusions}
\label{sec:concl}

We posed and studied the NCDN-mangament problem where content distribution and traffic engineering decisions can be optimized jointly by a single entity. %This paradigm is of key importance to \ncp s who own and manage the infrastructure for content distribution as well as the underlying network. 
Our trace-driven experiments using extensive access logs from the world's largest CDN and real ISP topologies resulted in the following key conclusions. First, simple \unplanned\ schemes for routing and placement of NCDN content, such as InverseCap and LRU, outperform sophisticated, joint-optimal placement and routing schemes based on recent historic demand. Second,  NCDN traffic demand can be ``shaped'' by effective content placement to the extent that the value of engineering routes for NCDN traffic is small.  Third, we studied the value of the future knowledge of demand for placement and routing decisions. While future knowledge helps, what is perhaps surprising is that a small amount of additional storage allows simple, \unplanned\ schemes to perform as well as \planned\ ones with future knowledge. Finally, with a mix of NCDN and transit traffic, the benefit of traditional traffic engineering is commensurate to the fraction of traffic that is transit traffic, i.e., ISPs dominated by NCDN traffic can simply make do with static routing schemes.  Overall, our findings suggest that content placement is a powerful degree of freedom that NCDNs can leverage to simplify and enhance traditional traffic engineering.

>>>>

\section{Conclusions}
\label{sec:concl-ncdn}

We posed and studied the NCDN-mangament problem where content delivery and traffic engineering decisions can be optimized jointly by a single entity. %This paradigm is of key importance to \ncp s who own and manage the infrastructure for content distribution as well as the underlying network. 
Our trace-driven experiments using extensive access logs from the world's largest CDN and real ISP topologies resulted in the following key conclusions. First, simple \unplanned\ schemes for routing and placement of NCDN content, such as InvCap and LRU, outperform sophisticated, joint-optimal placement and routing schemes based on recent historic demand. Second,  NCDN traffic demand can be ``shaped'' by effective content placement to the extent that the value of engineering routes for NCDN traffic is small.  Third, we studied the value of the future knowledge of demand for placement and routing decisions. While future knowledge helps, what is perhaps surprising is that a small amount of additional storage allows simple, \unplanned\ schemes to perform as well as \planned\ ones with future knowledge. Finally, with a mix of NCDN and transit traffic, the benefit of traditional traffic engineering is commensurate to the fraction of traffic that is transit traffic, i.e., ISPs dominated by NCDN traffic can simply make do with static routing schemes.  Overall, our findings suggest that content placement is a powerful degree of freedom that NCDNs can leverage to simplify and enhance traditional traffic engineering.

### 2015-07-14 ncdnpaper/Evaluation.tex
first complete version after fixing most of the stuff

\textbf{\invlru} uses LRU as the cache replacement strategy and InverseCap  (with ECMP) as the routing strategy. InverseCap is a static, shortest-path routing scheme where link weights are set to the inverse of the link capacity.  This scheme requires no information of either the content demand or the traffic matrix. If content is available at multiple PoPs, we choose the closest PoP based on hop count distance. We break  ties randomly among PoPs with equal hop count distance.

@@

 \textbf{\optlru} uses an \unplanned\  placement, LRU, but it uses an \planned, optimized routing that is updated  every three hours. The routing is computed by solving a multi-commodity flow problem 
 identical to  the traditional traffic engineering problem \cite{fortz2000internet}. We assume that the \ncp\ measures the traffic matrix over the preceding  three hours and computes routes that optimize the MLU for that matrix. The matrix incorporates the effect of the \unplanned\  placement and the implicit assumption is that the content demand and \unplanned\  placement result in a traffic matrix that does not change dramatically from one monitoring interval to the next---an assumption that also underlies traffic engineering as practiced by ISPs today.

@@

To determine the value of optimizing routing alone, we study the \textbf{\invoptpfuture} scheme. This is a variant of \optrpfuture\ where InverseCap routing is used and content placement is optimized, rather than jointly optimizing both. This scheme is computed  using the MIP formulation in Section \ref{sec:linearprograms} but with an additional constraint modification that ensures that InvCap routing is implemented.
%(refer to \cite{techreport} for the modified MIP formulation).

@@

\eat
{
To determine the value of optimizing routing alone, we study two more schemes: \textbf{\invoptp}  and \textbf{\invoptpfuture}. One can view these as variants of \optrp\  and \optrpfuture\ respectively where InverseCap routing is used and content placement is optimized, rather than performing a joint optimization of both. These schemes use a simple variant  from the MIP described in Section \ref{sec:linearprograms}, which restricts the MIP to follow InverseCap routing. A complete description is presented in  \cite{techreport}.
}
%define the values of the decision variable $f_{ije}$ that determines the routing  as per InvCap, and solve the MIP for other decision variables.

@@

%To answer this question, we compared \invlru\ with  \optlru\ and \optrpfuture\ with \invoptpfuture. 
How are the above conclusions impacted if  \invlru\  were to optimize routing or   \optrpfuture\  were to use InverseCap routing? To answer this question, we analyze the maximum reduction in MLU by using \optlru\ over \invlru\ across all storage ratios in Figure  \ref{fig:mlureduction}. We similarly compare \optrpfuture\ and \invoptpfuture.   We find that \optlru\ improves the MLU over  \invlru\ by at most 10\% across all traces suggesting that optimizing routing is of little value for an \unplanned\  placement scheme.   \optrpfuture\  reduces the network cost by at most 13\% compared to \invoptpfuture. As we consider \optrpfuture\ to be the ``ideal'' scheme with full future knowledge, these results show that the best MLU can be achieved by optimizing content placement alone; optimizing routing adds little additional value.

>>>>

\textbf{\invlru} uses LRU as the cache replacement strategy and InvCap  (with ECMP) as the routing strategy. InvCap is a static, shortest-path routing scheme where link weights are set to the inverse of the link capacity.  This scheme requires no information of either the content demand or the traffic matrix. If content is available at multiple PoPs, we choose the closest PoP based on hop count distance. We break  ties randomly among PoPs with equal hop count distance.

@@

 \textbf{\optlru} uses a \unplanned\  placement, LRU, but it uses an \planned, optimized routing that is updated  every three hours. The routing is computed by solving a multi-commodity flow problem 
 identical to  the traditional traffic engineering problem \cite{fortz2000internet}. We assume that the \ncp\ measures the traffic matrix over the preceding  three hours and computes routes that optimize the MLU for that matrix. The matrix incorporates the effect of the \unplanned\  placement and the implicit assumption is that the content demand and \unplanned\  placement result in a traffic matrix that does not change dramatically from one monitoring interval to the next---an assumption that also underlies traffic engineering as practiced by ISPs today.

@@

To determine the value of optimizing routing alone, we study the \textbf{\invoptpfuture} scheme. This is a variant of \optrpfuture\ where InvCap routing is used and content placement is optimized, rather than jointly optimizing both. This scheme is computed  using the MIP formulation in Section \ref{sec:linearprograms} but with an additional constraint modification that ensures that InvCap routing is implemented.
%(refer to \cite{techreport} for the modified MIP formulation).

@@

\eat
{
To determine the value of optimizing routing alone, we study two more schemes: \textbf{\invoptp}  and \textbf{\invoptpfuture}. One can view these as variants of \optrp\  and \optrpfuture\ respectively where InvCap routing is used and content placement is optimized, rather than performing a joint optimization of both. These schemes use a simple variant  from the MIP described in Section \ref{sec:linearprograms}, which restricts the MIP to follow InvCap routing. A complete description is presented in  \cite{techreport}.
}
%define the values of the decision variable $f_{ije}$ that determines the routing  as per InvCap, and solve the MIP for other decision variables.

@@

%To answer this question, we compared \invlru\ with  \optlru\ and \optrpfuture\ with \invoptpfuture. 
How are the above conclusions impacted if  \invlru\  were to optimize routing or   \optrpfuture\  were to use InvCap routing? To answer this question, we analyze the maximum reduction in MLU by using \optlru\ over \invlru\ across all storage ratios in Figure  \ref{fig:mlureduction}. We similarly compare \optrpfuture\ and \invoptpfuture.   We find that \optlru\ improves the MLU over  \invlru\ by at most 10\% across all traces suggesting that optimizing routing is of little value for an \unplanned\  placement scheme.   \optrpfuture\  reduces the network cost by at most 13\% compared to \invoptpfuture. As we consider \optrpfuture\ to be the ``ideal'' scheme with full future knowledge, these results show that the best MLU can be achieved by optimizing content placement alone; optimizing routing adds little additional value.
